Title Goes Here

### 2024-04-02 analysis/paper/paper.qmd
update raw data

ggsave(here("analysis",
            "figures", 
            "fig-requirements-per-year.png"),
       bg ="white")

@@

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
           # position=position_jitter(w=0.05, h=0.0),
            se = FALSE) +
  geom_point(data = jobdata_topic_year_tally_max,
             aes(year_ad_posted,
                 prop,
                 group = name,
                 colour = name),
             size = 10) +
  geom_text_repel(data = jobdata_topic_year_tally_max,
                  aes(year_ad_posted,
                      prop ,
                      group = name,
                      colour = name,
                      label = name),
                  nudge_y = 0.01,
                  bg.color = "white",
                  bg.r = 0.25,
                  size = 3) +
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()

>>>>

ggsave(here("analysis",
            "figures", 
            "fig-requirements-per-year.png"),
       bg ="white",
       h = 5, # experiment with h and w to get the right size and proportion 
       w = 8,
       units = "in",
       dpi = 600) # make the image nice and crisp

@@

ggplot() +
  geom_smooth(data =  jobdata_topic_year_tally,
            aes(year_ad_posted,
                prop,
                group = name,
                colour = name),
            size = 2,
           # n = 10,
           span = 0.7,
           # position=position_jitter(w=0.05, h=0.0),
            se = FALSE) +
  # geom_point(data = jobdata_topic_year_tally_max,
  #            aes(year_ad_posted,
  #                prop,
  #                group = name,
  #                colour = name),
  #            size = 10) +
  # geom_text_repel(data = jobdata_topic_year_tally_max,
  #                 aes(year_ad_posted,
  #                     prop ,
  #                     group = name,
  #                     colour = name,
  #                     label = name),
  #                 nudge_y = 0.01,
  #                 bg.color = "white",
  #                 bg.r = 0.25,
  #                 size = 3) +
  # explore direct labels
  xlab("Year") +
  ylab("Proportion of all ads") +
  theme_minimal()
